---
title: "Combine networks"
author: Alexis Hucteau
date: "`r Sys.Date()`"
output:
    html_document:
      toc: yes
      toc_float: yes
      theme: united
editor_options:
  markdown:
    wrap: sentence
  chunk_output_type: inline
---

# Libraries

```{r, error=F, warning=F, echo=FALSE, include=F}
rm(DmIALite, DOLite, DOLiteTerm, HsIALite, MmIALite, RnIALite)

library(dplyr)
library(parallel)
cores2Use <- detectCores()

"%ni%" <- Negate("%in%")
```

# Create Intra layer links

## Functions

```{r}
Formattage_layers <- function(Layer, n){
  Layer <- Layer[1:3]
  colnames(Layer) <- c("from", "to", "weight")
  Layer$layer_from <- rep(n, nrow(Layer))
  Layer$layer_to <- rep(n, nrow(Layer))
  Layer <- Layer[, c("from", "layer_from", "to", "layer_to", "weight")]
  Layer[Layer$weight !=0,]
}

Intra_layer_links <- function(Layer_1, Layer_2, Layer_3, Layer_4){
  layers.list <- list(Layer_1, Layer_2, Layer_3, Layer_4)
  layers.list <- mclapply(1:4, function(layer){
    Formattage_layers(layers.list[[layer]], layer)
  }, mc.cores = cores2Use)
  
  intra_links <- purrr::reduce(layers.list, rbind) %>%
    unique
  
  unique_nodes <- c(intra_links$from, intra_links$to) %>%
    unique
  
  id_conversion <- data.frame(id_node = 1:length(unique_nodes),
                              label_node = unique_nodes)
  
  intra_links <- merge(intra_links, id_conversion, by.x = "from", by.y = "label_node", all.x = T)
  intra_links$from <- intra_links$id_node
  intra_links <- intra_links[,c("from", "layer_from", "to", "layer_to", "weight")]
  intra_links <- merge(intra_links, id_conversion, by.x = "to", by.y = "label_node", all.x = T)
  intra_links$to <- intra_links$id_node
  intra_links <- intra_links[,c("from", "layer_from", "to", "layer_to", "weight")]
  
  list("Intra_links" = intra_links, "ID_conversion" = id_conversion)
}
```

## Layer tests

```{r, eval=F}
layer_test_1 <- read.delim("~/GitHub/Thesis_paper/Scripts/Making_Phenotype_multilayer_network_scripts/Multi_test/Test_multi_interlayer/layer_test_1.csv", header=F)
layer_test_1_conversion <- read.delim("~/GitHub/Thesis_paper/Scripts/Making_Phenotype_multilayer_network_scripts/Multi_test/Test_multi_interlayer/layer_test_1_conversion.csv", header=F)
layer_test_2 <- read.delim("~/GitHub/Thesis_paper/Scripts/Making_Phenotype_multilayer_network_scripts/Multi_test/Test_multi_interlayer/layer_test_2.csv", header=F)
layer_test_3 <- read.delim("~/GitHub/Thesis_paper/Scripts/Making_Phenotype_multilayer_network_scripts/Multi_test/Test_multi_interlayer/layer_test_3.csv", header=F)
layer_test_4 <- read.delim("~/GitHub/Thesis_paper/Scripts/Making_Phenotype_multilayer_network_scripts/Multi_test/Test_multi_interlayer/layer_test_4.csv", header=F)
layer_test_4_conversion <- read.delim("~/GitHub/Thesis_paper/Scripts/Making_Phenotype_multilayer_network_scripts/Multi_test/Test_multi_interlayer/layer_test_4_conversion.csv", header=F)

test <- Intra_layer_links(layer_test_1, layer_test_2, layer_test_3, layer_test_4)
```

## Real layers

```{r}
Top_weighted <- function(Network, N_top){
  last_col <- ncol(Network)
  Network <- Network[order(Network[last_col], decreasing = T),]
  Network[1:N_top,]
}
```

# All links multi layer intra scaled

```{r}
Folder_multilayers <- "~/GitHub/Thesis_paper/Results/Multi_layer_pheno_like/Final_mutlilayer/"
Phenos <- c("mIDH1_R", "mIDH1_NR", "mIDH2_R", "mIDH2_NR") 

Layers_All_links_multi_layer_intra_scaled <- lapply(Phenos, function(Pheno){
  pheno_folder <- paste0(Folder_multilayers, Pheno, "/")
  layer_1 <- read.table(paste0(pheno_folder, "Layer_1/Network.tsv"), 
                        sep = "\t", header = T)
  layer_1$weight <- layer_1$weight %>% as.numeric
  layer_2 <- read.table(paste0(pheno_folder, "Layer_2/", Pheno, "_GRN_network.tsv"),
                        sep = "\t", header = T) %>%
    .[c(1,2,5)]
  layer_2$weight_corr <- layer_2$weight_corr %>% as.numeric

  layer_3 <- read.table(paste0(pheno_folder, "Layer_3/PPI.tsv"),
                        sep = "\t", header = T) 
  layer_3$weight <- layer_3$weight %>% as.numeric
  
  layer_4 <- read.table(paste0(pheno_folder, "Layer_4/", Pheno, "_Reactions_weighted.tsv"),
                        sep = "\t", header = T, quote = "\"") 
  layer_4$scaled_weight <- layer_4$scaled_weight %>% as.numeric

  Intra_layer_links(layer_1, layer_2, layer_3, layer_4)
})
names(Layers_All_links_multi_layer_intra_scaled) <- Phenos
```

# Create Custom Inter layer links

## Functions

```{r}
Create_Custom_Inter_layer_links <- function(Intra_layer, Layer_conversion, layer){
  frag_in_network <- dplyr::filter(Layer_conversion, V1 %in% Intra_layer[["ID_conversion"]]$label_node)
  gene_not_in_ID_conversion <- Layer_conversion$V2[Layer_conversion$V2 %ni% Intra_layer[["ID_conversion"]]$label_node] %>% unique
  new_ids <- max(Intra_layer[["ID_conversion"]]$id_node) + 1
  new_ids_max <- new_ids + length(gene_not_in_ID_conversion) - 1
  new_ids_range <- new_ids:new_ids_max
  gene_not_in_ID_conversion <- data.frame("Node_label" = gene_not_in_ID_conversion, 
                                          "Node_ID" = new_ids_range)
  tmp <- mclapply(1:nrow(frag_in_network), function(ele){
    id_to <- dplyr::filter(Intra_layer[["ID_conversion"]], label_node %in% frag_in_network[ele, "V2"]) %>%
    .$id_node 
    id_from <- dplyr::filter(Intra_layer[["ID_conversion"]], label_node %in% frag_in_network[ele, "V1"]) %>%
    .$id_node 
    if(length(id_to) == 0){
      new_gene_data <- dplyr::filter(gene_not_in_ID_conversion, Node_label == frag_in_network[ele, "V2"])
      new_node_id <- new_gene_data$Node_ID
      new_node_label <- new_gene_data$Node_label
      layer_to <- ifelse(layer == 1, 2, 3)
      new_edge <- data.frame("from" = id_from, "layer_from" = layer, 
                 "to" = new_node_id, "layer_to" = layer_to, 
                 "weight" = 0.5)
      new_ID <- data.frame("id_node" = new_node_id, "label_node" = new_node_label)
    }else{
      layer_to <- ifelse(layer == 1, 2, 3)
      new_edge <- data.frame("from" = id_from, "layer_from" = layer, 
                   "to" = id_to, "layer_to" = layer_to, 
                   "weight" = 0.5)
      new_ID <- NULL
    }
    list("Intra_links" = new_edge, "ID_conversion" = new_ID)
  }, mc.cores = 8) 
  new_intra_links <- mclapply(1:length(tmp), function(new_id){
    tmp[[new_id]][["Intra_links"]]
  }, mc.cores = cores2Use) %>% data.table::rbindlist() %>% unique %>% data.frame
  new_id_converted <- mclapply(1:length(tmp), function(new_id){
    tmp[[new_id]][["ID_conversion"]]
  }, mc.cores = cores2Use) %>% data.table::rbindlist() %>% unique %>% data.frame
  links <- rbind(Intra_layer[["Intra_links"]], new_intra_links) %>% unique
  ID_conversion <- rbind(Intra_layer[["ID_conversion"]], new_id_converted) %>% unique
  
  if(layer == 4){
    inter_links <- Add_inter_links_of_common_nodes(links, ID_conversion)
  }else{
    inter_links <- links
  }
  
  list("Intra_links" = inter_links, "ID_conversion" = ID_conversion)
}

Add_inter_links_of_common_nodes <- function(Links, Nodes){
  nodes_layers <- mclapply(2:3, function(Layers){
    node.from <- dplyr::filter(Links, layer_from == Layers) %>% .$from
    node.to <- dplyr::filter(Links, layer_to == Layers) %>% .$to
    unique(c(node.from, node.to))
  }, mc.cores = cores2Use)
  common_nodes <- intersect(nodes_layers[[1]], nodes_layers[[2]])
  if(!is.null(common_nodes)){
    new_links <- mclapply(common_nodes, function(Nodes){
      data.frame("from" = common_nodes, "layer_from" = 2, 
                 "to" = common_nodes, "layer_to" = 3, 
                 "weight" = 0.75
                 )
    }, mc.cores = cores2Use) %>% data.table::rbindlist() %>% unique
  }else{
    new_links <- data.frame()
  }
  rbind(Links, new_links)
}
```

## Data conversion

```{r}
layer_1_dataconversion <- read.table("~/GitHub/Thesis_paper/Datasets/Chromatine_part/Associate_fragment_to_gene_promoter.tsv",
                                 sep = "\t", header = T)
colnames(layer_1_dataconversion) <- c("V1", "V2")

layer_4_dataconversion <- read.table("~/GitHub/Thesis_paper/Datasets/Metabolic_datasets/Gene_reactions_network.tsv",
                                     sep = "\t", header = T)
colnames(layer_4_dataconversion) <- c("V1", "V2")
```

```{r}
Inter_layered <- lapply(Phenos, function(Pheno){
  res <- Create_Custom_Inter_layer_links(Layers_All_links_multi_layer_intra_scaled[[Pheno]], layer_1_dataconversion, 1)
  res <- Create_Custom_Inter_layer_links(res, layer_4_dataconversion, 4)
  res
})
names(Inter_layered) <- Phenos
```


```{r, eval = F}
save.image("/media/alexis/DATA/Session/R_session/Thesis_paper_Rsessions/Multi_layer_phenolike/Directed_multi_layer.RData")
system("bash ~/shutdown_o_clock.sh")
```

# Scale intralayer connections

```{r}
Make_intra_scaled_link <- function(Link_line, intra_weight){
  if(Link_line$layer_from < Link_line$layer_to){
    res <-data.frame("from" = c(Link_line$from, Link_line$to), 
             "layer_from" = c(Link_line$layer_from, Link_line$layer_to),
             "to" = c(Link_line$to, Link_line$from), 
             "layer_to" = c(Link_line$layer_to, Link_line$layer_from), 
             "weight" = c(intra_weight[[Link_line$layer_from]][[1]], 
                          intra_weight[[Link_line$layer_from]][[2]]))
  }else{
    res <- data.frame("from" = c(Link_line$from, Link_line$to), 
               "layer_from" = c(Link_line$layer_from, Link_line$layer_to),
               "to" = c(Link_line$to, Link_line$from), 
               "layer_to" = c(Link_line$layer_to, Link_line$layer_from), 
               "weight" = c(intra_weight[[Link_line$layer_to]][[2]], 
                          intra_weight[[Link_line$layer_to]][[1]]))
  }
  return(res)
}


Scaling_intralayer_connection <- function(Multilayer){
  layer_network <- lapply(1:4, function(layer){
    dplyr::filter(Multilayer[["Intra_links"]], layer_from == layer & layer_to == layer) %>%
      .[c(1,3)] %>% unique %>% igraph::graph.data.frame(directed = F) %>%
      igraph::degree(mode = "all") %>% summary
  })
  
  intra_layer_links <- lapply(1:3, function(intra){
    n_nodes_in <- layer_network[[intra]][[3]]
    n_nodes_out <- layer_network[[intra + 1]][[3]]
    in2out <- n_nodes_in/n_nodes_out
    in2out <- (1-1/(in2out+1))
    in2out <- 0.2+0.6*in2out
    out2in <- n_nodes_out/n_nodes_in 
    out2in <- (1-1/(out2in+1))
    out2in <- 0.2+0.6*out2in
    list(in2out, out2in)
  }) 
  intra_links <- dplyr::filter(Multilayer[["Intra_links"]], layer_from != layer_to)
  new_intra_links <- lapply(1:nrow(intra_links), function(link){
    Make_intra_scaled_link(intra_links[link,], intra_layer_links)
  }) %>% data.table::rbindlist() %>% unique
  inter_links <- dplyr::filter(Multilayer[["Intra_links"]], layer_from == layer_to)
  rbind(inter_links, new_intra_links)
}

```

```{r}
x <- seq(1:10)
x_low <- 1/x
x <- c(x_low, x) %>% .[order(., decreasing = F)]
y <- 0.2+0.6*(1-(1/(x+1)))
z <- 0.2+0.6*(1-(1/((1/x)+1)))
plot(x,y, type = "l", col = "red", ylim = c(0.2, 0.8), xlab = "Rapport de densité couche A / couche B", ylab = "poids inter-layer")
lines(x = x, y = z, col = "blue")
legend("topleft", c("Poids couche A vers B","Poids couche B vers A"), fill=c("blue","red"))
```
```{r}
Multi_layers_scaled <- mclapply(names(Inter_layered), function(Multi_layer){
  ID_conversion <- Inter_layered[[Multi_layer]][["ID_conversion"]]
  Intra_links <- Scaling_intralayer_connection(Inter_layered[[Multi_layer]])
  list("ID_conversion" = ID_conversion, "Intra_links" = Intra_links)
}, mc.cores = 2)

names(Multi_layers_scaled) <- Phenos
```

```{r}
Folder_multilayers <- "~/GitHub/Thesis_paper/Results/Multi_layer_pheno_like/Final_mutlilayer/"

Make_Multilayer_file <- function(Multilayer, Class){
  vertices <- Multilayer[[Class]][["ID_conversion"]]
  multilayer <- Multilayer[[Class]][["Intra_links"]]
  multilayer <- multilayer[,c(2,1,4,3,5)]
  
  dir.create(paste0(Folder_multilayers, Class), showWarnings = F)
  n_vertices <- unique(vertices$id_node) %>% length
  n_edges <- nrow(multilayer)
  file_edge <- paste0(Folder_multilayers, Class, "/", Class, "_multilayer_infomap.edges")
  if(file.exists(file_edge)){
    file.remove(file_edge)
  }
  fileConn <- file(file_edge, open = "at")
  writeLines(c(paste("*Vertices", n_vertices), "# node_id name"), fileConn)
  utils::write.table(
      vertices,
      file = fileConn,
      row.names = F,
      col.names = F,
      quote = F
    )
  intra <- dplyr::filter(multilayer, layer_from == layer_to)
  n_intra <- nrow(intra)
  writeLines(c(paste("*Multilayer", n_edges), "# layer_id node_id layer_id node_id weight", paste("# intra", n_intra)), fileConn)
  inter <- dplyr::filter(multilayer, layer_from != layer_to)
  n_inter <- nrow(inter)
  utils::write.table(
      intra,
      file = fileConn,
      row.names = F,
      col.names = F,
      quote = F
    )
  writeLines(paste("# inter", n_inter), fileConn)
  utils::write.table(
      inter,
      file = fileConn,
      row.names = F,
      col.names = F,
      quote = F
    )
  close(fileConn)
  multilayer %>%
    write.table(paste0(Folder_multilayers, Class, "/", Class, "_multilayer_infomap.tsv"), sep = "\t", row.names = F)
  vertices %>%
    write.table(paste0(Folder_multilayers, Class, "/", Class, "_multilayer_infomap_vertices.tsv"), sep = "\t", row.names = F)
  return(NULL)
}
```

```{r}
mclapply(names(Multi_layers_scaled), function(Class){
  Make_Multilayer_file(Multi_layers_scaled, Class)
  NULL
}, mc.cores = cores2Use)
```

```{r}
system("bash ./Send_multilayer_to_genologin.sh")
```














```{r}
Folder_multilayers

trash <- mclapply(names(Multi_layers_scaled), function(multi){
  dir.create(paste0(Folder_multilayers, "/Scaled_intra_links_v2/"), showWarnings = F)
  dir.create(paste0(Folder_multilayers, "/Scaled_intra_links_v2/", multi), showWarnings = F)
  Multi_layers_scaled[[multi]][["ID_conversion"]] %>%
  write.table(paste0(Folder_multilayers, "/Scaled_intra_links_v2/", multi, "/layout.txt"),
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
  Multi_layers_scaled[[multi]][["Intra_links"]] %>%
  write.table(paste0(Folder_multilayers, "/Scaled_intra_links_v2/", multi, "/Multilayer.edges"),
              sep = " ", col.names=FALSE, quote = F, row.names = F)
  folder_Pheno <- paste0("~/GitHub/Thesis_paper/Results/Multi_layer_pheno_like/Scaled_intra_links_v2/", multi, "/")
  config_file <- paste0(folder_Pheno, "Multilayer.edges;", folder_Pheno, "layers.txt;", folder_Pheno, "layout.txt")
  config_path <- paste0(folder_Pheno, "config.txt")
  fileConn <- file(config_path)
  writeLines(config_file, fileConn)
  close(fileConn)
  layers_file <- c("layerID layerLabel", 
                   "1 3D_chromatin_network", 
                   "2 Gene_regulatory_network", 
                   "3 Functionnal_Protein_protein_network", 
                   "4 Metabolic_network")
  layers_path <- paste0(folder_Pheno, "layers.txt")
  fileConn <- file(layers_path)
  writeLines(layers_file, fileConn)
  close(fileConn)
})
rm(trash)
```


# Create layer 1 to layer 4 links

## Function

```{r, eval = F}
Make_crossed_links <- function(Vector_A, Vector_B){
  mclapply(Vector_A, function(frag){
    mclapply(Vector_B, function(react){
      data.frame("from" = frag, "layer_from" = 1, "to" = react, "layer_to" = 4, "weight" = 1)
    }, mc.cores = cores2Use) %>% data.table::rbindlist() %>% unique
  }, mc.cores = cores2Use) %>% data.table::rbindlist() %>% unique
}

Create_layer_1_to_layer_4_links <- function(Intra_layer, Layer_1_conversion, Layer_4_conversion){
  frag_in_network <- dplyr::filter(Layer_1_conversion, V1 %in% Intra_layer[["ID_conversion"]]$label_node)
  reaction_in_network <- dplyr::filter(Layer_4_conversion, V1 %in% Intra_layer[["ID_conversion"]]$label_node)
  
  gene_associated_to_frag <- frag_in_network$V2 %>% unique
  gene_associated_to_reaction <- reaction_in_network$V2 %>% unique
  
  genes_associated_to_frag_n_reaction <- intersect(gene_associated_to_frag, gene_associated_to_reaction)
  new_intra_links <- mclapply(genes_associated_to_frag_n_reaction, function(gene){
    frag_label <- dplyr::filter(frag_in_network, V2 == gene) %>% .$V1
    react_label <- dplyr::filter(reaction_in_network, V2 == gene) %>% .$V1
    frag_ids <- dplyr::filter(Intra_layer[["ID_conversion"]], label_node %in% frag_label) %>% .$id_node
    react_ids <- dplyr::filter(Intra_layer[["ID_conversion"]], label_node %in% react_label) %>% .$id_node
    Make_crossed_links(frag_ids, react_ids) 
  }, mc.cores = cores2Use) %>% data.table::rbindlist() %>% unique
  rbind(Intra_layer[["Intra_links"]], new_intra_links) %>% unique
}
```

### Cluster NR

```{r}
message(date())
# Cluster_NR_multilayer[["Intra_links"]] <- Create_layer_1_to_layer_4_links(Cluster_NR_multilayer, layer_1_dataconversion, layer_4_dataconversion)
```

### Cluster R

```{r}
message(date())
# Cluster_R_multilayer[["Intra_links"]] <- Create_layer_1_to_layer_4_links(Cluster_R_multilayer, layer_1_dataconversion, layer_4_dataconversion)
```

### mIDH1

```{r}
message(date())
# mIDH1_multilayer[["Intra_links"]] <- Create_layer_1_to_layer_4_links(mIDH1_multilayer, layer_1_dataconversion, layer_4_dataconversion)
```

### mIDH2

```{r}
message(date())
# mIDH2_multilayer[["Intra_links"]] <- Create_layer_1_to_layer_4_links(mIDH2_multilayer, layer_1_dataconversion, layer_4_dataconversion)
message(date())
```

# Saving multilayers and ID_converter

## ARACNe GRN no filter

### Cluster_NR

```{r, eval = F}
Cluster_NR_multilayer[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_NR/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_NR_multilayer[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_NR/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### Cluster_R

```{r, eval = F}
Cluster_R_multilayer[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_R/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_R_multilayer[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_R/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### mIDH1

```{r, eval = F}
mIDH1_multilayer[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH1/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

mIDH1_multilayer[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH1/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### mIDH2

```{r, eval = F}
mIDH2_multilayer[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH2/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

mIDH2_multilayer[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH2/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

## Filtered Layers

### Cluster_NR

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_NR_filtered/Multi_layer/")

Cluster_NR_multilayer_filtered[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_NR_filtered/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_NR_multilayer_filtered[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_NR_filtered/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### Cluster_R

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_R_filtered/Multi_layer/")

Cluster_R_multilayer_filtered[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_R_filtered/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_R_multilayer_filtered[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_R_filtered/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### mIDH1

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/mIDH1_filtered/Multi_layer/")

mIDH1_multilayer_filtered[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH1_filtered/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

mIDH1_multilayer_filtered[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH1_filtered/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### mIDH2

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/mIDH2_filtered/Multi_layer/")

mIDH2_multilayer_filtered[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH2_filtered/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

mIDH2_multilayer_filtered[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH2_filtered/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

## Sub multilayer

### Cluster IDH1 R

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH1_R/Multi_layer", showWarnings = F)
  
Cluster_mIDH1_R_multilayer_filtered[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH1_R/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_mIDH1_R_multilayer_filtered[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH1_R/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### Cluster IDH2 R

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH2_R/Multi_layer", showWarnings = F)

Cluster_mIDH2_R_multilayer_filtered[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_R/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_mIDH2_R_multilayer_filtered[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_R/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### Cluster IDH2 NR

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH2_NR/Multi_layer", showWarnings = F)

Cluster_mIDH2_NR_multilayer_filtered[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_NR/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_mIDH2_NR_multilayer_filtered[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_NR/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

##25k Filtered Layers 25k

### Cluster_NR

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_NR_filtered_25k/", showWarnings = F)
dir.create("../../Results/Multi_layer_pheno_like/Cluster_NR_filtered_25k/Multi_layer/", showWarnings = F)

Cluster_NR_multilayer_filtered_25k[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_NR_filtered_25k/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_NR_multilayer_filtered_25k[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_NR_filtered_25k/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### Cluster_R

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_R_filtered_25k/", showWarnings = F)
dir.create("../../Results/Multi_layer_pheno_like/Cluster_R_filtered_25k/Multi_layer/", showWarnings = F)

Cluster_R_multilayer_filtered_25k[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_R_filtered_25k/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_R_multilayer_filtered_25k[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_R_filtered_25k/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### mIDH1

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/mIDH1_filtered_25k/", showWarnings = F)
dir.create("../../Results/Multi_layer_pheno_like/mIDH1_filtered_25k/Multi_layer/", showWarnings = F)

mIDH1_multilayer_filtered_25k[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH1_filtered_25k/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

mIDH1_multilayer_filtered_25k[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH1_filtered_25k/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### mIDH2

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/mIDH2_filtered_25k/", showWarnings = F)
dir.create("../../Results/Multi_layer_pheno_like/mIDH2_filtered_25k/Multi_layer/", showWarnings = F)

mIDH2_multilayer_filtered_25k[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH2_filtered_25k/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

mIDH2_multilayer_filtered_25k[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/mIDH2_filtered_25k/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

## Sub multilayer

### Cluster IDH1 R

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH1_R_25k", showWarnings = F)
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH1_R_25k/Multi_layer", showWarnings = F)

Cluster_mIDH1_R_multilayer_filtered_25k[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH1_R_25k/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_mIDH1_R_multilayer_filtered_25k[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH1_R_25k/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### Cluster IDH2 R

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH2_R_25k", showWarnings = F)
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH2_R_25k/Multi_layer", showWarnings = F)

Cluster_mIDH2_R_multilayer_filtered_25k[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_R_25k/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_mIDH2_R_multilayer_filtered_25k[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_R_25k/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

### Cluster IDH2 NR

```{r, eval = F}
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH2_NR_25k", showWarnings = F)
dir.create("../../Results/Multi_layer_pheno_like/Cluster_IDH2_NR_25k/Multi_layer", showWarnings = F)

Cluster_mIDH2_NR_multilayer_filtered_25k[["Intra_links"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_NR_25k/Multi_layer/Multilayer.edges",
              sep = " ", col.names=FALSE, quote = F, row.names = F)

Cluster_mIDH2_NR_multilayer_filtered_25k[["ID_conversion"]] %>%
  write.table("../../Results/Multi_layer_pheno_like/Cluster_IDH2_NR_25k/Multi_layer/layout.txt",
              sep = " ", col.names = c("nodeID", "nodeLabel"), quote = F, row.names = F)
```

```{r, eval = F}
save.image("/media/alexis/DATA/Session/R_session/Thesis_paper_Rsessions/Multi_layer_phenolike/Combined_layers.RData")
system("bash ~/shutdown_o_clock.sh")
```

# Connectivity for each layer and each pheno

```{r}
Calculate_degree_distribution_function <- function(Multi_layer){
  layer_network <- lapply(1:4, function(layer){
    dplyr::filter(Multi_layer[["Intra_links"]], layer_from == layer & layer_to == layer) %>%
      .[c(1,3)] %>% unique %>% igraph::graph.data.frame(directed = F) %>%
      igraph::degree(mode = "all")
  })
}



```

```{r, eval = F}
Degree_ditrib <- list()

Degree_ditrib[["Cluster_mIDH2_NR_degree"]] <- Calculate_degree_distribution_function(Cluster_mIDH2_NR_multilayer_filtered)
Degree_ditrib[["Cluster_mIDH2_NR_degree_25k"]] <- Calculate_degree_distribution_function(Cluster_mIDH2_NR_multilayer_filtered_25k)
Degree_ditrib[["Cluster_mIDH2_R_degree"]] <- Calculate_degree_distribution_function(Cluster_mIDH2_R_multilayer_filtered)
Degree_ditrib[["Cluster_mIDH2_R_degree_25k"]] <- Calculate_degree_distribution_function(Cluster_mIDH2_R_multilayer_filtered_25k)
Degree_ditrib[["Cluster_NR_degree"]] <- Calculate_degree_distribution_function(Cluster_NR_multilayer_filtered)
Degree_ditrib[["Cluster_N_degree_25k"]] <- Calculate_degree_distribution_function(Cluster_NR_multilayer_filtered_25k)
Degree_ditrib[["Cluster_R_mIDH1_degree"]] <- Calculate_degree_distribution_function(Cluster_R_mIDH1_multilayer_filtered)
Degree_ditrib[["Cluster_R_mIDH1_degree_25k"]] <- Calculate_degree_distribution_function(Cluster_R_mIDH1_multilayer_filtered_25k)
Degree_ditrib[["Cluster_R_degree"]] <- Calculate_degree_distribution_function(Cluster_R_multilayer_filtered)
Degree_ditrib[["Cluster_R_degree_25k"]] <- Calculate_degree_distribution_function(Cluster_R_multilayer_filtered_25k)
Degree_ditrib[["mIDH1_degree"]] <- Calculate_degree_distribution_function(mIDH1_multilayer_filtered)
Degree_ditrib[["mIDH1_degree_25k"]] <- Calculate_degree_distribution_function(mIDH1_multilayer_filtered_25k)
Degree_ditrib[["mIDH2_degree"]] <- Calculate_degree_distribution_function(mIDH2_multilayer_filtered)
Degree_ditrib[["mIDH2_degree_25k"]] <- Calculate_degree_distribution_function(mIDH2_multilayer_filtered_25k)

```

```{r, eval = F}
lapply(names(Degree_ditrib), function(multilayer){
  par(mfrow=c(2,2))
  lapply(1:4, function(l){
    density(log(Degree_ditrib[[multilayer]][[l]])) %>% plot(main = paste0("layer ", l)) 
  })
  mtext(multilayer, side = 3, line = -25, outer = TRUE)
})

```
