---
title: "Making Phenotype multilayer network"
subtitle: "Layer 4"
author: Alexis Hucteau
date: "`r Sys.Date()`"
output:
    html_document:
      toc: yes
      toc_float: yes
      theme: united
editor_options:
  markdown:
    wrap: sentence
---

# Libraries

```{r, error=F, warning=F, echo=FALSE, include=F}
rm(DmIALite, DOLite, DOLiteTerm, HsIALite, MmIALite, RnIALite)

library(dplyr)
library(matrixTests)
library(factoextra)
library(Hmisc)
library(matrixStats)
library(RColorBrewer)
library(pheatmap)
library(data.table)
library(parallel)

cores2use <- detectCores()


source("~/Core_scripts/core_functions.R")
```

# Loading data

## Reaction dataset

```{r}
mIDHi_react_scores_GEM <- read.csv("../../Datasets/mIDHi_react_scores_GEM.csv", check.names = F, row.names = 1)
colnames(mIDHi_react_scores_GEM) <- colnames(mIDHi_react_scores_GEM) %>%
  stringr::str_remove("X")
Clinical_patient_data <- read.table("../../Datasets/Clinical_Koichi_data_isoform.tsv", sep = "\t", header = T)
Clinical_patient_data$Baseline_phenotype_2 <- sapply(Clinical_patient_data$Best_response, function(resp){
  switch(resp,
         "CR" = "Responder",
         "CRp" = "Responder",
         "CRi" = "Responder",
         "MLFS" = "Overall_Responder",
         "HI" = "Overall_Responder",
         "PR" = "Overall_Responder",
         "SD" = "Non_Responder",
         "PD" = "Non_Responder",
         "Not_assessed" = "Not_assessed",
         "NA" = "Control")
})
```

## Split data into classes

```{r}
Pheno_classes <- colnames(mIDHi_react_scores_GEM) %>% lapply(function(sample){
  fil <- Clinical_patient_data %>%
    dplyr::filter(Baseline_RNAseq_data == sample)
  data.frame("IDH" = fil$IDH_isoform, "Cluster" = fil$Cluster, 
             "sample" = fil$Baseline_RNAseq_data, "Response" = fil$Baseline_phenotype_2)
}) %>% data.table::rbindlist()


Samples_NR <- Pheno_classes %>% dplyr::filter(Response == "Non_Responder") %>% .$sample
Samples_R <- Pheno_classes %>% dplyr::filter(Response == "Responder") %>% .$sample

Samples_mIDH1 <- Pheno_classes %>% dplyr::filter(IDH == "IDH1") %>% .$sample
Samples_mIDH2 <- Pheno_classes %>% dplyr::filter(IDH == "IDH2_R140" | IDH == "IDH2_R172" | IDH == "IDH2") %>% .$sample

Samples_IDH1_R <- Pheno_classes %>% dplyr::filter(Response == "Responder" & IDH == "IDH1") %>% .$sample
Samples_IDH1_NR <- Pheno_classes %>% dplyr::filter(Response == "Non_Responder" & IDH == "IDH1") %>% .$sample

Samples_IDH2_R <- Pheno_classes %>% dplyr::filter(Response == "Responder" & (IDH == "IDH2_R140" | IDH == "IDH2_R172" | IDH == "mIDH2")) %>% .$sample
Samples_IDH2_NR <- Pheno_classes %>% dplyr::filter(Response =="Non_Responder"  & (IDH == "IDH2_R140" | IDH == "IDH2_R172")) %>% .$sample

Phenos_list <- list("mIDH1_R" = Samples_IDH1_R, "mIDH2_R" = Samples_IDH2_R, 
                    "mIDH2_NR" = Samples_IDH2_NR, "mIDH1_NR"= Samples_IDH1_NR)

Reactions <- lapply(names(Phenos_list), function(Phenos){
  mIDHi_react_scores_GEM[Phenos_list[[Phenos]]]
})
names(Reactions) <- names(Phenos_list)
```

## Loading metabolic network

```{r}
library(biomaRt)
Human_GEM <- read.csv("../../Datasets/Human_GEM_2.csv")
```




```{r}
Metabolic_network <- read.table("../../Datasets/Metabolic_network_clean.tsv",
                                sep = "\t", header = T)

From_reversible_equation_to_network <- function(Reactions_values, Reaction){
  In_reaction_values <- Reactions_values[stringr::str_detect(rownames(Reactions_values), paste0(Reaction$ID, "_pos")), ]
  if(nrow(In_reaction_values) ==0){
    In_reaction_values_zscore <- 0
    Out_reaction_values_zscore <- 0
  }else{
    In_reaction_values$mean <- rowMeans(In_reaction_values)
    In_reaction_values$sd <- matrixStats::rowVars(as.matrix(dplyr::select(In_reaction_values, -c("mean"))))
    In_reaction_values_zscore <- In_reaction_values$mean / In_reaction_values$sd
    
    Out_reaction_values <- Reactions_values[stringr::str_detect(rownames(Reactions_values), paste0(Reaction$ID, "_neg")), ]
    if(nrow(Out_reaction_values) ==0){
      Out_reaction_values_zscore <- 0
    }else{
      Out_reaction_values$mean <- rowMeans(Out_reaction_values)
      Out_reaction_values$sd <- matrixStats::rowVars(as.matrix(dplyr::select(Out_reaction_values, -c("mean"))))
      Out_reaction_values_zscore <- Out_reaction_values$mean / Out_reaction_values$sd
    }
  }
  
  equation <- Reaction$EQUATION
  in_metabolites <- stringr::str_split_i(equation, pattern = "<=>", 1) %>% 
    stringr::str_split(pattern = " \\+ ") %>% unlist %>% stringr::str_trim() %>% 
    sapply(function(test){
      first_element <- stringr::str_split_i(test, pattern = " ", 1)
      if(stringr::str_detect(first_element, "[a-z]")){
        test
      }else{
        coeff <- stringr::str_split(test, pattern = " ") %>% .[[1]] %>% length()
        if(coeff > 2){
          splitted <- stringr::str_split(test, pattern = " ") %>% unlist %>% .[2:coeff] %>% paste(collapse = "_")
          splitted
        }else{
          stringr::str_split_i(test, pattern = " ", coeff)
        }
      }
    }) %>% unname
  out_metabolites <- stringr::str_split_i(equation, pattern = "<=>", 2) %>% 
    stringr::str_split(pattern = " \\+ ") %>% unlist %>% stringr::str_trim()  %>% 
    sapply(function(test){
      first_element <- stringr::str_split_i(test, pattern = " ", 1)
      if(stringr::str_detect(first_element, "[a-z]")){
        test
      }else{
        coeff <- length(stringr::str_split(test, pattern = " ")[[1]])
        if(coeff > 2){
          splitted <- stringr::str_split(test, pattern = " ") %>% unlist %>% .[2:coeff] %>% paste(collapse = "_")
          splitted
        }else{
          stringr::str_split_i(test, pattern = " ", coeff)
        }
      }
    }) %>% unname %>% 
    ifelse(. == "", in_metabolites, .)
  
  
  in_reactions_data_frame <- lapply(in_metabolites, function(metabolite){
    data.frame("A" = metabolite, "B" = Reaction$ID, "weight" = In_reaction_values_zscore)
  }) %>% data.table::rbindlist()
  
  out_reaction_data_frame <- lapply(out_metabolites, function(metabolite){
    data.frame("A" = Reaction$ID, "B" = metabolite, "weight" = Out_reaction_values_zscore)
  }) %>% data.table::rbindlist()
  
  rbind(in_reactions_data_frame, out_reaction_data_frame)
}

From_irreversible_equation_to_network <- function(Reactions_values, Reaction){
  In_reaction_values <- Reactions_values[stringr::str_detect(rownames(Reactions_values), paste0(Reaction$ID, "_pos")), ]
  if(nrow(In_reaction_values) ==0){
    In_reaction_values_zscore <- 0
  }else{
    In_reaction_values$mean <- rowMeans(In_reaction_values)
    In_reaction_values$sd <- matrixStats::rowVars(as.matrix(dplyr::select(In_reaction_values, -c("mean"))))
    In_reaction_values_zscore <- In_reaction_values$mean / In_reaction_values$sd
  }
  equation <- Reaction$EQUATION
  in_metabolites <- stringr::str_split_i(equation, pattern = "=>", 1) %>% 
    stringr::str_split(pattern = " \\+ ") %>% unlist %>% stringr::str_trim() %>% 
    sapply(function(test){
      first_element <- stringr::str_split_i(test, pattern = " ", 1)
      if(stringr::str_detect(first_element, "[a-z]")){
        test
      }else{
        coeff <- length(stringr::str_split(test, pattern = " ")[[1]])
        if(coeff > 2){
          splitted <- stringr::str_split(test, pattern = " ") %>% unlist %>% .[2:coeff] %>% paste(collapse = "_")
          splitted
        }else{
          res <- stringr::str_split_i(test, pattern = " ", coeff)
          res
        }
      }
    }) %>% unname
  out_metabolites <- stringr::str_split_i(equation, pattern = "=>", 2) %>% 
    stringr::str_split(pattern = " \\+ ") %>% unlist %>% stringr::str_trim() %>% 
    sapply(function(test){
      if(stringr::str_detect(stringr::str_split_i(test, pattern = " ", 1), "[a-z]")){
        test
      }else{
        coeff <- length(stringr::str_split(test, pattern = " ")[[1]])
        if(coeff > 2){
          splitted <- stringr::str_split(test, pattern = " ") %>% unlist %>% .[2:coeff] %>% paste(collapse = "_")
          splitted
        }else{
          stringr::str_split_i(test, pattern = " ", coeff)
        }
      }
    }) %>% unname
  
  in_reactions_data_frame <- lapply(in_metabolites, function(metabolite){
    data.frame("A" = metabolite, "B" = Reaction$ID, "weight" = In_reaction_values_zscore)
  }) %>% data.table::rbindlist()
  
  out_reaction_data_frame <- lapply(out_metabolites, function(metabolite){
    data.frame("A" = Reaction$ID, "B" = metabolite, "weight" = In_reaction_values_zscore)
  }) %>% data.table::rbindlist()
  
  rbind(in_reactions_data_frame)
}

From_Pheno_reaction_values_to_metabolic_network <- function(Class, Network = Human_GEM){
  mclapply(1:nrow(Network), function(reaction){
    if(stringr::str_detect(Network[reaction, "EQUATION"], pattern = "<=>")){
      From_reversible_equation_to_network(Reactions[[Class]], Network[reaction, ])
    }else{
      From_irreversible_equation_to_network(Reactions[[Class]], Network[reaction, ])
    }
  }, mc.cores = cores2use) %>% data.table::rbindlist()
}
```

```{r}
Classes_networks <- lapply(names(Phenos_list), function(Pheno){
  From_Pheno_reaction_values_to_metabolic_network(Pheno)
})
names(Classes_networks) <- names(Phenos_list)
```


# Calculate mean zscore values

## Function

```{r}
# Calculate_values_through_samples <- function(Features){
#   res <- Features
#   res$mean <- rowMeans(res)
#   res$sd <- matrixStats::rowVars(as.matrix(Features))
#   res$zscore <- res$mean / res$sd
#   zscore_max <- max(res$zscore[res$zscore != Inf])
#   res$zscore <- sapply(res$zscore, function(zscore){
#     ifelse(zscore == Inf, zscore_max, zscore)
#   })
#   res
# }
```

## Calculate reactions values per classes

```{r}
# Reactions <- lapply(names(Reactions), function(Pheno){
#   Calculate_values_through_samples(Reactions[[Pheno]])
# })
# names(Reactions) <- names(Phenos_list)
```

```{r}
# plot(x = log10(Reactions[["R"]]$zscore), y = log10(Reactions[["NR"]]$zscore))
```

# Calculate edges weight

## Function

```{r}
Scale_edges_weight <- function(Network){
  w_no_inf <- Network$weight %>% .[. != Inf]
  zscore_IQR <- (quantile(na.omit(w_no_inf), 0.75) - quantile(na.omit(w_no_inf), 0.25)) * 1.5
  zscore_weight_max <- quantile(na.omit(w_no_inf), 0.75) + zscore_IQR
  w_min <- Network$weight %>% .[. != 0] %>% min
  res <- Network
  res$scaled_weight <- sapply(Network$weight, function(w){
    if(w > zscore_weight_max){
      1
    }else if(w == 0){
      0
    }else{
      log(w)/log(zscore_weight_max)
    }
  })
  res
}
```

```{r}
Classes_networks_scaled <- lapply(names(Classes_networks), function(Class){
  Scale_edges_weight(Classes_networks[[Class]])
})
names(Classes_networks_scaled) <- names(Classes_networks)
```

NO_DATA <- lapply(names(Pp_met_features), function(Pheno){
  d <- density(na.omit(Pp_met_features[[Pheno]]$mean))
  png(paste0("~/GitHub/Thesis_paper/Results/Multi_layer_pheno_like/Layer_Figures/Layer_1/", Pheno, "_methylations_values.png"))
  plot(d, main = Pheno)
  dev.off()
  plot(d, main = Pheno)

})


```{r}
lapply(names(Classes_networks_scaled), function(Class){
  png(paste0("~/GitHub/Thesis_paper/Results/Multi_layer_pheno_like/Layer_Figures/Layer_4/", Class, "_reactions_values.png"))
  p <- Classes_networks_scaled[[Class]] %>%  .$scaled_weight %>% density %>% plot(main = Class)
  dev.off()
  p
})
```

```{r}
Plotting_function <- function(A, B, title, xlabel, ylabel){
  a_no_null_weight <- A$weight !=0 & A$scaled_weight != 1
  b_no_null_weight <- B$weight !=0 & B$scaled_weight != 1
  no_null <- (a_no_null_weight | b_no_null_weight)
  a <- A[no_null,]
  b <- B[no_null,]
  df <- data.frame(x = (a$scaled_weight), y = (b$scaled_weight))
  d <- MASS::kde2d(df$x, df$y)
  dens <- data.frame(expand.grid(x = d$x, y = d$y), z = as.vector(d$z))
  plot_final <- ggplot() +
    geom_contour_filled(data = dens, aes(x=x, y=y, z =z, alpha = after_stat(level))) +
    theme(legend.position = "none") + xlab(xlabel) + ylab(ylabel)                     
    ggsave(paste0("~/GitHub/Thesis_paper/Results/Multi_layer_pheno_like/Layer_Figures/Layer_4/", title, "_Cross_weight.png"), plot_final, height = 2100, width = 2100, units = "px")
  plot_final
}
```

```{r}
Plotting_function(Classes_networks_scaled[["mIDH1_NR"]], Classes_networks_scaled[["mIDH1_R"]], "Response in IDH1", "mIDH1 Non responder", "mIDH1 Responder")
Plotting_function(Classes_networks_scaled[["mIDH2_NR"]], Classes_networks_scaled[["mIDH2_R"]], "Response in IDH2", "mIDH2 Non responder", "mIDH2 Responder")
Plotting_function(Classes_networks_scaled[["mIDH2_R"]], Classes_networks_scaled[["mIDH1_R"]], "IDH in Responder", "mIDH2 Responder", "mIDH1 Responder")
Plotting_function(Classes_networks_scaled[["mIDH2_NR"]], Classes_networks_scaled[["mIDH1_NR"]], "IDH in Non responder", "mIDH2 Non responder", "mIDH1 Non responder")
```




```{r, eval = F}
Calculate_edges_weight <- function(Features, Network = Metabolic_network){
  pos_features <- dplyr::filter(Features, stringr::str_detect(rownames(Features), pattern = "_pos"))
  rownames(pos_features) <- stringr::str_remove(rownames(pos_features), pattern = "_pos")

  neg_features <- dplyr::filter(Features, stringr::str_detect(rownames(Features), pattern = "_neg"))
  rownames(neg_features) <- stringr::str_remove(rownames(neg_features), pattern = "_neg")
  res <- mclapply(1:nrow(Network), function(interaction){
    a <- Network[interaction, "A"]
    b <- Network[interaction, "B"]
    if(a %in% rownames(neg_features)){
      data.frame("source" = a,
                 "target" = b,
                 "weight_zscore" = pos_features[a, "zscore"] + neg_features[a, "zscore"] /2,
                 "weight_mean" = pos_features[a, "mean"] + neg_features[a, "mean"] / 2)
    }else{
      data.frame("source" = a,
               "target" = b,
               "weight_zscore" = pos_features[a, "zscore"],
               "weight_mean" = pos_features[a, "mean"])
    }
  }, mc.cores = cores2use) %>% data.table::rbindlist()
  res$weight_zscore <- log10(res$weight_zscore)
  mean_IQR <- (quantile(na.omit(res$weight_mean), 0.75) - quantile(na.omit(res$weight_mean), 0.25)) * 1.5
  zscore_IQR <- (quantile(na.omit(res$weight_zscore), 0.75) - quantile(na.omit(res$weight_zscore), 0.25)) * 1.5
  mean_weight_max <- quantile(na.omit(res$weight_mean), 0.75) + mean_IQR
  zscore_weight_max <- quantile(na.omit(res$weight_zscore), 0.75) + zscore_IQR
  med_mean_weight <- quantile(na.omit(res$weight_mean), 0.5)
  med_zscore <- quantile(na.omit(res$weight_zscore), 0.5)
  res$weight_mean_scaled <- sapply(res$weight_mean, function(w){
    if(is.na(w)){
      med_mean_weight / mean_weight_max
    }else if(w > mean_weight_max){
      1
    }else{
      w / mean_weight_max
    }
  })
  res$weight_zscore_scaled <- sapply(res$weight_zscore, function(w){
    if(is.na(w)){
      med_zscore / zscore_weight_max
    }else if(w > zscore_weight_max){
      1
    }else{
      w / zscore_weight_max
    }
  })
  res
}
```





## Calculs

```{r, eval = F}
Reactions_weighted <- mclapply(names(Reactions), function(Pheno){
  Calculate_edges_weight(Reactions[[Pheno]], Metabolic_network)
}, mc.cores = cores2use)
names(Reactions_weighted) <- names(Reactions)

```

## Density plots

```{r, eval = F}
lapply(names(Reactions_weighted), function(Pheno){
  plot(density(na.omit(Reactions_weighted[[Pheno]]$weight_zscore_scaled)))
})
```

```{r, eval = F}
Reactions_weighted <- mclapply(names(Reactions_weighted), function(Pheno){
  tmp <- Reactions_weighted[[Pheno]]
  tmp$target <- stringr::str_replace_all(tmp$target, pattern = " ", replacement = "_")
  tmp
}, mc.cores = cores2use)
names(Reactions_weighted) <- names(Reactions)
```

```{r, eval = F}
Top_weighted <- function(Metabo_net, N_top){
  Metabo_net <- Metabo_net[order(Metabo_net$weight_zscore_scaled, decreasing = T),]
  Metabo_net[1:N_top,]
}
```

# Saving networks

```{r}
Folder_mulilayer <- "~/GitHub/Thesis_paper/Results/Multi_layer_pheno_like/Final_mutlilayer/"

NULL_lapply <- lapply(names(Classes_networks_scaled), function(Pheno){
  dir.create(paste0(Folder_mulilayer, Pheno), showWarnings = F)
  dir.create(paste0(Folder_mulilayer, Pheno, "/Layer_4"), showWarnings = F)
  Classes_networks_scaled[[Pheno]][,c(1,2,4)] %>%
    write.table(paste0(Folder_mulilayer, "/", Pheno, "/Layer_4/", Pheno, "_Reactions_weighted.tsv"),
              sep = "\t", quote = F, row.names = F)
})
rm(NULL_lapply)
```

