---
title: "Network single layer analysis and figure"
author: Alexis Hucteau
date: "`r Sys.Date()`"
output:
    html_document:
      toc: yes
      toc_float: yes
      theme: united
editor_options:
  markdown:
    wrap: sentence
---

```{r}
rm(DmIALite, DOLite, DOLiteTerm, HsIALite, MmIALite, RnIALite)
```

# Library

```{r}
library(RCy3)
library(dplyr)
library(igraph)
library(ggplot2)
library(ComplexHeatmap)
library(sva)

```

# *Data importation Layer 1*

## KOICHI Cluster 1 vs Cluster 2 

### PCHIC

```{r}
Cluster_KOICHI_Pchic_network_path = "~/GitHub/Thesis_paper/Results/Chromatine_part/Chromatine_networks/Pchic_Koichi_Clusters.tsv"

Cluster_KOICHI_Pchic_network <- read.table(Cluster_KOICHI_Pchic_network_path, sep = "\t", header = T)
```

### HSC

```{r}
Cluster_KOICHI_HSC_network_path = "~/GitHub/Thesis_paper/Results/Chromatine_part/Chromatine_networks/HSC_KOICHI_Clusters.tsv"

Cluster_KOICHI_HSC_network <- read.table(Cluster_KOICHI_HSC_network_path, sep = "\t", header = T)
```

## KOICHI mIDH1 vs mIDH2

### PCHIC

```{r}
mIDH_KOICHI_Pchic_network_path = "~/GitHub/Thesis_paper/Results/Chromatine_part/Chromatine_networks/Pchic_KOICHI_mIDH.tsv"

mIDH_KOICHI_Pchic_network <- read.table(mIDH_KOICHI_Pchic_network_path, sep = "\t", header = T)
```

### HSC

```{r}
mIDH_KOICHI_HSC_network_path = "~/GitHub/Thesis_paper/Results/Chromatine_part/Chromatine_networks/HSC_KOICHI_mIDH.tsv"

mIDH_KOICHI_HSC_network <- read.table(mIDH_KOICHI_HSC_network_path, sep = "\t", header = T)
```

# *Data importation Layer 2*

## KOICHI Cluster 1 vs Cluster 2

```{r}
Cluster_ARACNe_KOICHI_path <- "~/GitHub/Thesis_paper/Results/Network_4_Multilayer/Filtered_GRN_network.tsv"
Cluster_ARACNe_KOICHI_network <- read.table(Cluster_ARACNe_KOICHI_path, sep = "\t", header = T)
```



## KOICHI mIDH1 vs mIDH2

```{r}
mIDH_ARACNe_KOICHI_path <- "~/GitHub/Thesis_paper/Results/GRN/Network/ARACNe/IDHs_Koichi_msvip_ARACNe_network.tsv"
mIDH_ARACNe_KOICHI_network <- read.table(mIDH_ARACNe_KOICHI_path, sep = "\t", header = T)
```


# *Data importation Layer 3*

## KOICHI Cluster 1 vs Cluster 2

```{r}
mIDH_fPPI_KOICHI_path <- "~/GitHub/Thesis_paper/Results/fPPI/Annotations_cleaned_for_multi_layer.tsv"
mIDH_fPPI_KOICHI_network <- read.table(mIDH_fPPI_KOICHI_path, sep = "\t", header = T)
```


## KOICHI mIDH1 vs mIDH2

```{r}
Cluster_fPPI_KOICHI_path <- "~/GitHub/Thesis_paper/Results/Proteo/PPI_filtered_005_enhanced.tsv"
Cluster_fPPI_KOICHI_network <- read.table(Cluster_fPPI_KOICHI_path, sep = "\t", header = T)
```

# *Data importation Layer 4*

## KOICHI Cluster 1 vs Cluster 2

```{r}
Metabo_gene_KOICHI_path <- "~/GitHub/Thesis_paper/Results/Metabolism/Gene_reactions_network.tsv"
Metabo_gene_KOICHI_network <- read.table(Metabo_gene_KOICHI_path, sep = "\t", header = T)
```

# *Data importation Layer 5*

## KOICHI Cluster 1 vs Cluster 2

```{r}
Clusters_Metabo_KOICHI_path <- "~/GitHub/Thesis_paper/Results/Metabolism/Metabolic_network_clean_filtered_Clusters.tsv"
Clusters_Metabo_KOICHI_network <- read.table(Clusters_Metabo_KOICHI_path, sep = "\t", header = T)
```

## KOICHI mIDH1 vs mIDH2

```{r}
mIDH_Metabo_KOICHI_path <- "~/GitHub/Thesis_paper/Results/Metabolism/Metabolic_network_clean_filtered_KOICHI_IDHm.tsv"
mIDH_Metabo_KOICHI_network <- read.table(mIDH_Metabo_KOICHI_path, sep = "\t", header = T)
```

# Network analysis functions

## Do_single_layer_network_analysis

```{r}
Do_single_layer_network_analysis <- function(network){
  inet <- graph_from_data_frame(network, directed = F)
  
  t_inet <- igraph::reverse_edges(inet)
  eigen_centrality_result <- eigen_centrality(t_inet, directed = T)$vector %>% as.data.frame
  page_rank_result <- igraph::page_rank(inet, directed = T)$vector %>% as.data.frame
  degree_result <- igraph::degree(inet) %>% as.data.frame
  closenessness_result <- igraph::closeness(inet) %>% as.data.frame
  betweenness_result <- igraph::betweenness(inet, directed = F) %>% as.data.frame
  
  feature_df <- data.frame(ID = names(V(inet)))
  
  feature_df <- merge(feature_df, eigen_centrality_result, by.x = "ID", by.y = 0, all.x = T)
  colnames(feature_df)[2] <- "eigenvalue"
  feature_df <- merge(feature_df, page_rank_result, by.x = "ID", by.y = 0, all.x = T)
  colnames(feature_df)[3] <- "Page_Rank"
  feature_df <- merge(feature_df, degree_result, by.x = "ID", by.y = 0, all.x = T)
  colnames(feature_df)[4] <- "degree"
  feature_df <- merge(feature_df, closenessness_result, by.x = "ID", by.y = 0, all.x = T)
  colnames(feature_df)[5] <- "closeness"
  feature_df <- merge(feature_df, betweenness_result, by.x = "ID", by.y = 0, all.x = T)
  colnames(feature_df)[6] <- "betweenness"
  
  feature_df
}
```

## Do_plot_function

```{r}
Do_plot_function <- function(network, x_axis, y_axis, feature = NULL){
  if(is.null(feature)){
    feature <- Do_single_layer_network_analysis(network)
  }
  feature <- dplyr::filter(feature, stringr::str_detect(ID, pattern = "[:alpha:]") & !stringr::str_detect(ID, pattern = "\\["))
  nudgex <- (max(feature[deparse(substitute(x_axis))]) - min(feature[deparse(substitute(x_axis))]))/12
  ggplot(feature, aes(x = {{x_axis}}, y = {{y_axis}}, label = ID))+
    geom_text(check_overlap = T, size = 4, nudge_x = -nudgex, hjust = 0, outlier.size = 0)+
    geom_point(size = 0.5)+
    labs(title = paste0("Network-based node prioritization ", deparse(substitute(network))))+
    xlab(deparse(substitute(x_axis)))+
    ylab(deparse(substitute(y_axis)))
}
```

# Network analysis Layer 1

## mIDH Pchic

```{r}
# Do_single_layer_network_analysis(mIDH_KOICHI_Pchic_network)
Do_plot_function(mIDH_KOICHI_Pchic_network, degree, Page_Rank)
Do_plot_function(mIDH_KOICHI_Pchic_network, degree, betweenness)

```

## mIDH HSC

```{r}
# Do_single_layer_network_analysis(mIDH_KOICHI_Pchic_network)
Do_plot_function(mIDH_KOICHI_HSC_network, degree, Page_Rank)
Do_plot_function(mIDH_KOICHI_HSC_network, degree, betweenness)

```

## Cluster Pchic

```{r}
# Do_single_layer_network_analysis(mIDH_KOICHI_Pchic_network)
Do_plot_function(Cluster_KOICHI_Pchic_network, degree, Page_Rank)
Do_plot_function(Cluster_KOICHI_Pchic_network, degree, betweenness)

```

## Cluster HSC

```{r}
# Do_single_layer_network_analysis(mIDH_KOICHI_Pchic_network)
Do_plot_function(Cluster_KOICHI_HSC_network, degree, Page_Rank)
Do_plot_function(Cluster_KOICHI_HSC_network, degree, betweenness)

```


# Network analysis Layer 2

## mIDH

```{r}
mIDH_ARACNe_KOICHI_network_analysed <- Do_single_layer_network_analysis(mIDH_ARACNe_KOICHI_network)

Do_plot_function(mIDH_ARACNe_KOICHI_network, degree, Page_Rank, mIDH_ARACNe_KOICHI_network_analysed)
Do_plot_function(mIDH_ARACNe_KOICHI_network, degree, betweenness, mIDH_ARACNe_KOICHI_network_analysed)
Do_plot_function(mIDH_ARACNe_KOICHI_network, eigenvalue, Page_Rank, mIDH_ARACNe_KOICHI_network_analysed)

```

## Clusters

```{r}
Do_plot_function(Cluster_ARACNe_KOICHI_network, degree, Page_Rank)
Do_plot_function(Cluster_ARACNe_KOICHI_network, degree, betweenness)
```

# Network analysis Layer 3

## mIDH

```{r}
mIDH_fPPI_KOICHI_network_analysed <- Do_single_layer_network_analysis(mIDH_fPPI_KOICHI_network)


Do_plot_function(mIDH_fPPI_KOICHI_network, degree, Page_Rank, mIDH_fPPI_KOICHI_network_analysed)
Do_plot_function(mIDH_fPPI_KOICHI_network, degree, betweenness, mIDH_fPPI_KOICHI_network_analysed)
```

## Clusters

```{r}
Clusters_fPPI_KOICHI_network_analysed <- Do_single_layer_network_analysis(Cluster_fPPI_KOICHI_network)

Do_plot_function(Cluster_fPPI_KOICHI_network, degree, Page_Rank, Clusters_fPPI_KOICHI_network_analysed)
Do_plot_function(Cluster_fPPI_KOICHI_network, degree, betweenness, Clusters_fPPI_KOICHI_network_analysed)
```


# Network analysis Layer 4

```{r}
Metabo_KOICHI_network_analysed <- Do_single_layer_network_analysis(Metabo_gene_KOICHI_network)

Do_plot_function(mIDH_Metabo_gene_KOICHI_network, degree, Page_Rank, Metabo_KOICHI_network_analysed)
Do_plot_function(mIDH_Metabo_gene_KOICHI_network, degree, betweenness, Metabo_KOICHI_network_analysed)
```

# Network analysis Layer 5

## mIDH

```{r}
mIDH_Metabo_KOICHI_network_analysed <- Do_single_layer_network_analysis(mIDH_Metabo_KOICHI_network)

Do_plot_function(mIDH_Metabo_KOICHI_network, degree, Page_Rank, mIDH_Metabo_KOICHI_network_analysed)
Do_plot_function(mIDH_Metabo_KOICHI_network, degree, betweenness, mIDH_Metabo_KOICHI_network_analysed)
```

## Clusters

```{r}
Clusters_Metabo_KOICHI_network_analysed <- Do_single_layer_network_analysis(Clusters_Metabo_KOICHI_network)

Do_plot_function(Clusters_Metabo_KOICHI_network, degree, Page_Rank, Clusters_Metabo_KOICHI_network_analysed)
Do_plot_function(Clusters_Metabo_KOICHI_network, degree, betweenness, Clusters_Metabo_KOICHI_network_analysed)
```

# Upset Analysis

## Data importation

### mIDH

```{r}
mIDH_flow_data_feature_layer_1 <- read.table("../../Results/Multi_layer_IDHm_Koichi/Results/1_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(DNA_methylation_P.Value < 0.05 & abs(DNA_methylation_logFC) > 0.1)

mIDH_flow_data_feature_layer_2 <- read.table("../../Results/Multi_layer_IDHm_Koichi/Results/2_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(GRN_pval < 0.05)

mIDH_flow_data_feature_layer_3 <- read.table("../../Results/Multi_layer_IDHm_Koichi/Results/3_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(fPPI_IDH2_vs_IDH1_p.val < 0.05)

mIDH_flow_data_feature_layer_4 <- read.table("../../Results/Multi_layer_IDHm_Koichi/Results/4_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(Metabolism_pvalue < 0.05 )

mIDH_flow_data_feature_layer_5 <- read.table("../../Results/Multi_layer_IDHm_Koichi/Results/5_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(Metabolism_pvalue < 0.05)
```

### Clusters

```{r}
Clusters_flow_data_feature_layer_1 <- read.table("../../Results/Multi_layer_1/Results/1_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(DNA_methylation_P.Value < 0.05 & abs(DNA_methylation_logFC) > 0.1)

Clusters_flow_data_feature_layer_2 <- read.table("../../Results/Multi_layer_1/Results/2_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(GRN_pval < 0.05)

Clusters_flow_data_feature_layer_3 <- read.table("../../Results/Multi_layer_1/Results/3_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T)

Clusters_flow_data_feature_layer_4 <- read.table("../../Results/Multi_layer_1/Results/4_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(Metabolism_pvalue < 0.05 )

Clusters_flow_data_feature_layer_5 <- read.table("../../Results/Multi_layer_1/Results/5_layer_Best_flows_converted.tsv", 
                                             sep = "\t", header = T) %>%
  dplyr::filter(Metabolism_pvalue < 0.05)
```

## Function

```{r}
Do_overlaps_TF_upsets <- function(List_of_samples, title){
  comb_mat <- ComplexHeatmap::make_comb_mat(List_of_samples)
  comb_mat <- comb_mat[colSums(comb_mat) >1]
  cs <- comb_size(comb_mat)

  ht <- ComplexHeatmap::UpSet(comb_mat, row_title = title, top_annotation = HeatmapAnnotation(
        "Intersections" = anno_barplot(cs, 
            ylim = c(0, max(cs)*1.1),
            border = FALSE, 
            gp = gpar(fill = "black"), 
            height = unit(4, "cm")
        ), 
        annotation_name_side = "left", 
        annotation_name_rot = 90))
  ht = draw(ht)
  od = column_order(ht)
  decorate_annotation("Intersections", {
      grid.text(cs[od], x = seq_along(cs), y = unit(cs[od], "native") + unit(2, "pt"), 
          default.units = "native", just = c("left", "bottom"), 
          gp = gpar(fontsize = 12, col = "#404040"), rot = 45)
  })
}
```


```{r}
Make_List_node_from_features <- function(layer_1, layer_2, layer_3, layer_4){
  list(
    layer_1 = layer_1$nodeLabel %>% .[stringr::str_detect(., pattern = "[:alpha:]")] %>% unique,
    layer_2 = layer_2$nodeLabel %>% unique,
    layer_3 = layer_3$nodeLabel %>% unique,
    layer_4 = layer_4$nodeLabel %>% unique)
}

Make_Upset_plot <- function(List_of_nodes, title){
  Do_overlaps_TF_upsets(List_of_nodes, title)
}
```

## mIDH

```{r}
Make_Upset_plot(Make_List_node_from_features(mIDH_flow_data_feature_layer_1, mIDH_flow_data_feature_layer_2, 
                mIDH_flow_data_feature_layer_3, mIDH_flow_data_feature_layer_4), 
                "mIDH overlaps")

intersect(mIDH_flow_data_feature_layer_1$nodeLabel, mIDH_flow_data_feature_layer_3$nodeLabel)
intersect(mIDH_flow_data_feature_layer_1$nodeLabel, mIDH_flow_data_feature_layer_2$nodeLabel)
intersect(mIDH_flow_data_feature_layer_3$nodeLabel, mIDH_flow_data_feature_layer_2$nodeLabel)
```

## Clusters

```{r}
Make_Upset_plot(Make_List_node_from_features(Clusters_flow_data_feature_layer_1, Clusters_flow_data_feature_layer_2, 
                data.frame(nodeLabel = c()), Clusters_flow_data_feature_layer_4), 
                "Cluster analysis")

intersect(Clusters_flow_data_feature_layer_1$nodeLabel, Clusters_flow_data_feature_layer_2$nodeLabel)
```

# Functions

```{r}
Make_List_node_from_networks <- function(List_of_network){
  lapply(List_of_network, function(net){
    c(net[,1], net[,2]) %>% .[stringr::str_detect(., pattern = "[:alpha:]")] %>% unique
  })
}

Make_Upset_plot <- function(List_of_nodes, title){
  Do_overlaps_TF_upsets(List_of_nodes, title)
}

All_intersect <- function(List_of_nodes){
  purrr::reduce(List_of_nodes, intersect)
}
```


## mIDH

```{r}
Make_Upset_plot(Make_List_node_from_networks(
  list(layer_1 = mIDH_KOICHI_Pchic_network, layer_2 = mIDH_ARACNe_KOICHI_network, layer_3 = mIDH_fPPI_KOICHI_network, layer_4 = Metabo_gene_KOICHI_network)), "mIDH")

All_intersect(Make_List_node_from_networks(list(layer_1 = mIDH_KOICHI_Pchic_network, layer_2 = mIDH_ARACNe_KOICHI_network, layer_3 = mIDH_fPPI_KOICHI_network, layer_4 = Metabo_gene_KOICHI_network)))
```


```{r}
purrr::reduce(Make_List_node_from_networks(list(mIDH_KOICHI_Pchic_network, mIDH_fPPI_KOICHI_network,  Metabo_gene_KOICHI_network)), intersect)
```

## Clusters

```{r}
Make_Upset_plot(Make_List_node_from_networks(
  list(layer_1 = Cluster_KOICHI_Pchic_network, layer_2 = Cluster_ARACNe_KOICHI_network, layer_3 = Cluster_fPPI_KOICHI_network, layer_4 = Metabo_gene_KOICHI_network)), "Clusters")

message("4 layers intersections")

purrr::reduce(Make_List_node_from_networks(list(Cluster_KOICHI_Pchic_network, Cluster_ARACNe_KOICHI_network, Cluster_fPPI_KOICHI_network, Metabo_gene_KOICHI_network)), intersect)

message("2, 3, 4 layers intersections")

purrr::reduce(Make_List_node_from_networks(list(Cluster_ARACNe_KOICHI_network, Cluster_fPPI_KOICHI_network, Metabo_gene_KOICHI_network)), intersect)

message("1, 2, 3 layers intersections")

purrr::reduce(Make_List_node_from_networks(list(Cluster_KOICHI_Pchic_network, Cluster_ARACNe_KOICHI_network, Cluster_fPPI_KOICHI_network)), intersect)
```

